Damage localization based on vibrations

### 2017-03-20 rapport/paper.tex
intro paper

The purpose of this work is the analysis of a particular data-driven damage localization method,
 namely the FRF interpolation method \cite{dilena2015damage}, and the development of a statistical extension of this method.
This paper is organized as follows. In section II we  present the existing methods (model-based and data driven methods), 
then in section III we detail the different models of vibrating structures and finally, in section IV we talk about the localization using FRF interpolation method and, finally,  its results in section V.

@@

\section{Models of vibrating structures}% or Physical models

\subsection{Finite element model}

\subsection{Continous-time state-space model} %(model parameters and reduction):

\subsection{Discrete-time state-space model} %(impulses response)

%Stockastic state-space models
%ARMA models
%Continuous time frequency-domain models
%Discrete time frequency-domain models

@@

@@

@@

>>>>

The purpose of this work is the analysis of a particular data-driven damage localization method,
 namely the FRF interpolation method \cite{dilena2015damage}. Our contribution is the development of a simulation to obtain acceleration measurement (which can run on several structures), a proposition of a variant of the FRF interpolation method, and the statistical analysis of the two methods.
This paper is organized as follows. In section II we  present the existing methods (model-based and data driven methods), 
then in section III we talk about the localization using FRF interpolation method, in section IV we detail the different models of vibrating structures used to obtain data and, finally, the experiences and its results in section V.

@@

@@

\subsection{The FRF interpolation method}

@@

\subsection{Models of vibrating structures}% or Physical models

\subsubsection{Finite element model}

\subsubsection{Continous-time state-space model} %(model parameters and reduction):

\subsubsection{Discrete-time state-space model} %(impulses response)

@@

\subsection{Beam}

We test our localization on another structure: a beam. We don't detail this model in this paper, we just use it to verify our methods. The damage is localized between the sensors 4 and 5.

Figure (\ref{beam_curve}) shows two FRF, one for the undamaged state and the second for the damaged one, at a fixed frequency. We can easily see there is an irregularity at the sensor 4.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\textwidth]{images/poutre_curve2.png}
  \caption{}
  \label{beam_curve}
\end{figure}

Figure (\ref{beam_error}) shows the computed error. We can see that there are only two sensors with a positiv error, which are the sensors 4 and 5. Thus, the localization is good.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\textwidth]{images/poutre_error.png}
  \caption{}
  \label{beam_error}
\end{figure}

\subsection{Quantification}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.4\textwidth]{images/quantification_without_noise_100.png}
  \caption{}
  \label{quant}
\end{figure}
